Pulling oral and IV data from CvTdb

### 2023-04-12 Working Rmds/pulling_oral_iv_data_cvtdb.Rmd
Evaluating residuals by RMSE, R-squared, and overall error SD. Evaluating TK stats by tmax, Cmax, AUC. All evaluations under combinations of the following fitting conditions: log-transform TRUE/FALSE, dose-normalization TRUE/FALSE, rescale time TRUE/FALSE. Residuals for each fitting condition also calculated in all of the following combinations: log-scale residuals TRUE/FALSE, dose-normalized residuals TRUE/FALSE. This way we can compare apples to apples.
Removing accidental inclusion of credentials (which in any case are now outdated)

Set environment variables for the user name, password, host, and dbname that will be used to connect. In Windows 10, go to the search bar in the menu and type "environment variables." A menu item should pop up that says "Edit the system environment variables." Click it. A window should pop up. On tab "Advanced " (where you should be already), there is a button "Environment Variables" in the lower right. Click it. Under "User variables for [YOURNAME]", the top window, click the "New" button. Add a variable and value and click "OK". Repeat clicking the "New" button and adding variables. I added the following system environment variables:

cvt_user = app_cvtdb
cvt_password = Svg=ZDZkzxX7R=+J
cvt_host = ccte-postgres-res.dmap-prod.aws.epa.gov
cvt_dbname = res_cvtdb

@@

```{r}
write.csv(cvt_data,
          paste0("../inst/ext/cvt_data_",
          this_date,
          ".csv"),
          row.names = FALSE)
```

>>>>

Set environment variables for the user name, password, host, and dbname that will be used to connect. In Windows 10, go to the search bar in the menu and type "environment variables." A menu item should pop up that says "Edit the system environment variables." Click it. A window should pop up. On tab "Advanced " (where you should be already), there is a button "Environment Variables" in the lower right. Click it. Under "User variables for [YOURNAME]", the top window, click the "New" button. Add a variable and value and click "OK". Repeat clicking the "New" button and adding variables.

@@

```{r}
this_date <- "2023_01_05"
write.csv(cvt_data,
          paste0("../inst/ext/cvt_data_",
          this_date,
          ".csv"),
          row.names = FALSE)
```
